I/O simulation model with Linux page cache, integration and evaluation in SimGrid framework

### 2020-06-30 paper_io_sim.tex
Some comments in methods

	\section{Method}
		In this section, we present our approach to model file read/write, 
		I/O in memory, data flushing and cache eviction mechanisms 
		implemented in Linux. 
		We also detail the design the simulators in order to simulate I/O activities 
		and the implementation in Python and SimGrid framework. 
		Finally, we describe some experimental scenarios to evaluate our model 
		with a Python simulator, a baseline SimGrid simulator, a simulator 
		with SimGrid integrated with our model, and the results from real pipelines.

@@

			In our I/O simulation model, we try to simulate the write back page cache 
			mechanisms including memory I/O, cache eviction and data flushing as we 
			believe that they are the most important factors that affect the I/O time. 
			We separate our model into components and encapsulate them in a 
			kernel-like layer described in Figure~\ref{fig:interaction}. 
			This layer consists of two main classes, MemoryManager and IOManager.
			MemoryManager is responsible for memory simulation, which includes 
			memory I/O, flushing, cache eviction, and exposed its functions 
			to IOManager. The IOController class models higher abstraction with the 
			simulation of file read and file write.
			With this layer, simulated applications can simply request for 
			file reads and file writes by calling functions of IOManager class 
			instead of calling directly to storage simulation models.

			\begin{figure}
   				\centering
   				\includegraphics[width=0.85\columnwidth]{figures/interaction.pdf}
   				\caption{The additional layer between user application layer and 
   				storage simulation models}\label{fig:interaction}
			\end{figure}

@@

			We model memory with capacity, read bandwidth and write bandwidth. 
			When data is read from or written to memory, the actual 
			read/write time is calculated with the amount of data and memory 
			read/write bandwidth:

@@

			where:
			\begin{itemize}
				\item $t_{mr}$ is time to read data from memory
				\item $t_{mw}$ is time to write data to memory
				\item $D$ is the amount of data to read/write
				\item $r_m$ is memory read bandwidth
				\item $w_m$ is memory write bandwidth
			\end{itemize}

>>>>

	\section{Method}
		In this section, we present our approach to model file read/write, 
		I/O in memory, data flushing and cache eviction mechanisms 
		implemented in the Linux kernel. 
		We also detail the design the simulators in order to simulate I/O activities 
		and the implementation in Python and SimGrid framework \tristan{check grammar}. 
		Finally, we describe experimental scenarios to evaluate our model using real applications and
		a Python simulator prototype, the current SimGrid simulator, our extension of SimGrid, and the results from real pipelines.

@@

			Our simulation model simulates the main mechanisms of the
			write-back page cache including memory I/O, cache eviction and
			data flushing. We separate our model in two components, the IO
			Controller and the Memory Manager, which together simulate I/O
			in the Linux kernel (Figure~\ref{fig:interaction}). The Memory
			Manager simulates memory I/O, flushing, and cache eviction, whereas the
			IO Controller simulates file read and file write.
			Simulated applications can simply request
			file reads and file writes from the IO Manager
			instead of calling simulated storage directly.

			\begin{figure}
   				\centering
   				\includegraphics[width=0.85\columnwidth]{figures/interaction.pdf}
   				\caption{Overview of the simulated write-back page cache}\label{fig:interaction}
			\end{figure}

@@

			We model memory with a capacity, a read bandwidth and a write bandwidth. 
			When data is read from or written to memory, the actual 
			read/write time is calculated with the amount of data and memory 
			read/write bandwidth:

@@

			where:
			\begin{itemize}
				\item $t_{mr}$ is the time to read data from memory
				\item $t_{mw}$ is the time to write data to memory
				\item $D$ is the amount of data to read/write
				\item $r_m$ is the memory read bandwidth
				\item $w_m$ is the  memory write bandwidth
			\end{itemize}

			\tristan{how about parallel accesses to memory? I think it would be a motivation to simualte memory as a storage device, 
			and leverage existing bandwidth sharing mechanisms in SimGrid. You could updated Fig 1 to include memory in the storage devices, and 
			explain in your Python simulator implementation that only a simplistic model of storage device is used (for both disk and memory).}
